---
title: "A corpus-based analysis of ongoing change in the adjective amplifier systems of Hong Kong, Philippine, and Indian English"
author: Martin Schweinberger
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: word_document
---

This document shows an analysis of adjective amplification in Irish English based on the Irish component of the International Corpus of English (ICE). 

In a first step, the session is prepared by clearing the work space, setting options, activating packages and functions, as well as loading relevant functions.

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
# clean current workspace
rm(list=ls(all=T))                                      
# load packages
library(dplyr)  
library(stringr)
# set options
options(stringsAsFactors = F)                           
options(scipen = 999) 
options(max.print=10000)
# define image directory
imageDirectory <- "images"   
# specify path to corpra
hkpath <- "D:\\Uni\\Korpora\\Original\\ICE Hong Kong"
phipath <- "D:\\Uni\\Korpora\\Original\\ICE Philippines\\Corpus"
indpath <- "D:\\Uni\\Korpora\\Original\\ICE India\\Corpus"
biohkpath <- "D:\\Uni\\Korpora\\Metadata/BiodataIceHongKong_new.txt"
biophipath <- "D:\\Uni\\Korpora\\Metadata/BiodataIcePhilippines.txt"
bioindpath <- "D:\\Uni\\Korpora\\Metadata/BiodataIceIndia.txt"
```

Define files

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
icehk_files <- list.files(hkpath, pattern = "[S|s]1[A|a].*.txt", full.names = T)
icephi_files <- list.files(phipath, pattern = "S1A.*.TXT", full.names = T)
iceind_files <- list.files(indpath, pattern = "[S|s]1[A|a].*.txt", full.names = T)
```

Load corpus: HK

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
icehk <- sapply(icehk_files, function(x){
  x <- scan(x, what = "char", sep = "", quote = "", quiet = T, skipNul = T)
  x <- paste(x, sep = " ", collapse = " ")
  x <- str_squish(x)
})
# inspect
str(icehk)
```

Load corpus: PHI

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
icephi <- sapply(icephi_files, function(x){
  x <- scan(x, what = "char", sep = "", quote = "", quiet = T, skipNul = T)
  x <- paste(x, sep = " ", collapse = " ")
  x <- str_squish(x)
})
# inspect
str(icephi)
```

Load corpus: IND

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
iceind <- sapply(iceind_files, function(x){
  x <- scan(x, what = "char", sep = "", quote = "", quiet = T, skipNul = T)
  x <- paste(x, sep = " ", collapse = " ")
  x <- str_squish(x)
})
# inspect
str(iceind)
```

Create corpus tibble: HK

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
icehk_df <- unlist(stringr::str_split(stringr::str_replace_all(icehk, "<ICE-HK:[S|s]1[A|a]-",
                                                               "~~~<ICE-HK:S1A-"), "~~~"))
# create df 
icehk_df <- tibble(1:length(icehk_df),
                  rep("ICE-HK", length(icehk_df)),
                  str_remove_all(icehk_df, "#.*"),
                  str_remove_all(icehk_df, ">.*"), 
                  icehk_df)
# add column names
icehk_df <- icehk_df %>%
  rename(Id = colnames(icehk_df)[1],
         Corpus = colnames(icehk_df)[2],
         File = colnames(icehk_df)[3],
         Speaker = colnames(icehk_df)[4],
         SpeechUnit = colnames(icehk_df)[5]) %>%
  mutate(File = str_remove_all(File, ".*:"),
         Speaker = str_remove_all(Speaker, ".*#"),
         ExtraCorpusSpeaker = ifelse(str_detect(Speaker, "^X") == T, 1, 0),
         Speaker = str_remove_all(Speaker, ".*:"),
         SpeechUnit = str_remove(SpeechUnit, ".*? "),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<unclear>.*?</unclear>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "<&>.*?</&>"),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<.*?>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "[^[:alnum:]=\\'\\.\\-\\? ]"),
         CleanSpeechUnit = str_squish(CleanSpeechUnit)) %>%
  filter(ExtraCorpusSpeaker == 0,
         CleanSpeechUnit != "",
         Speaker  != "") %>%
  select(-ExtraCorpusSpeaker)
# inspect
str(icehk_df)
```

Extract speech units and word counts: HK

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
WordCount_HK <- icehk_df %>%
  mutate(WordCount = str_count(CleanSpeechUnit, " ") +1) %>%
  group_by(File, Speaker) %>%
  summarise(SpeechUnitCount = n(),
            WordCount = sum(WordCount))
# inspect
head(WordCount_HK)
```

Create corpus tibble: PHI

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
icephi_df <- unlist(stringr::str_split(stringr::str_replace_all(icephi, "<ICE-PHI:[S|s]1[A|a]-",
                                                                "~~~<ICE-PHI:S1A-"), "~~~"))
# create df 
icephi_df <- tibble(1:length(icephi_df),
                  rep("ICE-PHI", length(icephi_df)),
                  str_remove_all(icephi_df, "#.*"),
                  str_remove_all(icephi_df, ">.*"), 
                  icephi_df)
# add column names
icephi_df <- icephi_df %>%
  rename(Id = colnames(icephi_df)[1],
         Corpus = colnames(icephi_df)[2],
         File = colnames(icephi_df)[3],
         Speaker = colnames(icephi_df)[4],
         SpeechUnit = colnames(icephi_df)[5]) %>%
  mutate(File = str_remove_all(File, ".*:"),
         Speaker = str_remove_all(Speaker, ".*#"),
         ExtraCorpusSpeaker = ifelse(str_detect(Speaker, "^X") == T, 1, 0),
         Speaker = str_remove_all(Speaker, ".*:"),
         SpeechUnit = str_remove(SpeechUnit, ".*? "),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<unclear>.*?</unclear>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "<&>.*?</&>"),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<.*?>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "[^[:alnum:]=\\'\\.\\-\\? ]"),
         CleanSpeechUnit = str_squish(CleanSpeechUnit)) %>%
  filter(ExtraCorpusSpeaker == 0,
         CleanSpeechUnit != "") %>%
  select(-ExtraCorpusSpeaker)
# inspect
str(icephi_df)
```

Create corpus tibble: IND

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
iceind_df <- unlist(stringr::str_split(stringr::str_replace_all(iceind, "<ICE-IND:[S|s]1[A|a]-",
                                                                "~~~<ICE-IND:S1A-"), "~~~"))
# create df 
iceind_df <- tibble(1:length(iceind_df),
                  rep("ICE-IND", length(iceind_df)),
                  str_remove_all(iceind_df, "#.*"),
                  str_remove_all(iceind_df, ">.*"), 
                  iceind_df)
# add column names
iceind_df <- iceind_df %>%
  rename(Id = colnames(iceind_df)[1],
         Corpus = colnames(iceind_df)[2],
         File = colnames(iceind_df)[3],
         Speaker = colnames(iceind_df)[4],
         SpeechUnit = colnames(iceind_df)[5]) %>%
  mutate(File = str_remove_all(File, ".*:"),
         Speaker = str_remove_all(Speaker, ".*#"),
         ExtraCorpusSpeaker = ifelse(str_detect(Speaker, "^X") == T, 1, 0),
         Speaker = str_remove_all(Speaker, ".*:"),
         SpeechUnit = str_remove(SpeechUnit, ".*? "),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<unclear>.*?</unclear>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "<&>.*?</&>"),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<.*?>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "[^[:alnum:]=\\'\\.\\-\\? ]"),
         CleanSpeechUnit = str_squish(CleanSpeechUnit)) %>%
  filter(ExtraCorpusSpeaker == 0,
         CleanSpeechUnit != "") %>%
  select(-ExtraCorpusSpeaker)
# inspect
str(iceind_df)
```

Load biodata

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
biohk <- read.delim(biohkpath, sep = "\t", header = T, quote = "\"", comment.char = "") %>%
  rename(File = Textcode,
         Speaker = Speaker.ID)
biophi <- read.delim(biophipath, sep = "\t", header = T, quote = "\"", comment.char = "") %>%
  rename(File = text.id,
         Speaker = spk.ref)
bioind <- read.delim(bioindpath, sep = "\t", header = T, quote = "\"", comment.char = "") %>%
  rename(File = text.id,
         Speaker = spk.ref)
#inspect
colnames(biohk); colnames(biophi); colnames(bioind)
```

Add biodata

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
icehk_info <- left_join(icehk_df, WordCount_HK, by = c("File", "Speaker"))
icehk_info <- left_join(icehk_info, biohk, by = c("File", "Speaker"))
icephi_info <- left_join(icephi_df, biophi, by = c("File", "Speaker"))
iceind_info <- left_join(iceind_df, bioind, by = c("File", "Speaker"))
```

Remove superfluous columns

```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
icehk_info <- icehk_info %>%
  select(-Old.File, -Text.Category, -Subtext, -Description.of.Contents, -Last.Name,
         -First.Name, -Chinese.Name, -Primary.Education, -Secondary.Education, 
         -Tertiary.Education, -Professional.Training, -Overseas.Experience, -Affiliations, 
         -Employer, -Recording.Place) %>%
  rename(Date = Recording.Date,
         Ethnicity = Ethnic.Group,
         L1 = Mother.Tongue,
         OtherLanguages = Other.Languages,
         EducationLevel = Educational.Level) %>%
  mutate(Date = str_remove_all(Date, ".*-"),
         Gender = ifelse(Gender == "f", "female", 
                  ifelse(Gender == "m", "male", Gender)))
icephi_info <- icephi_info %>%
  select(-id, -orig.id, -file.speaker.id, -subfile.id, -your.id, -text.category,
         -organizing.body, -first.name, -last.name, -copyright.statement, -recording.place) %>%
  rename(Date = recording.date,
         Gender = gender,
         Age = age,
         Nationality = nationality,
         L1 = mother.tongue,
         Occupation = occupation,
         EducationLevel = educational.level,
         SpeechUnitCount = speech.unit.count,
         WordCount = word.count) %>%
  mutate(Date = str_remove_all(Date, ".*-"),
         Date = str_remove_all(Date, "[:alpha:]"),
         Date = str_squish(Date))
iceind_info <- iceind_info %>%
  select(-id, -file.speaker.id, -subfile.id, -place.of.recording, -text.category, -file.wordcount,
         -communicative.situation, -organising.body, -copyright.statement, -communicative.role,
         -surname, -forenames, -affiliations, -free.comments, -birthplace, -audience.size,
         -no.of.participants, -relationship.of.participants) %>%
  rename(Date = date.of.recording,
         Age = age,
         Gender = gender,
         Nationality = nationality,
         EducationLevel = education,
         Occupation = occupation,
         L1 = mother.tongue,
         OtherLanguages = other.languages,
         SpeechUnitCount = speech.unit.count,
         WordCount = word.count)
# inspect
head(icehk_info, 3)#; head(icephi_info, 3); head(iceind_info, 3)

```

 Combine data into a single table
 
```{r amphkphi_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- merge(icehk_info, icephi_info, all = TRUE)
ice <- merge(ice, iceind_info, all = TRUE)
ice <- ice %>%
  arrange(Corpus, File, Id) %>%
  mutate(Date = str_remove_all(Date, ".* "),
         Date = ifelse(nchar(Date) == 2 & str_detect(Date, "^0"), paste("20", Date, sep = ""),
                ifelse(nchar(Date) == 2 & str_detect(Date, "^9"), paste("19", Date, sep = ""),
                       Date)),
         Date = str_replace_all(Date, "1993/94", "1993"),
         Age = ifelse(Age == "60 or above", "60+", Age))
# inspect
head(ice)
```
