---
title: "A corpus-based analysis of ongoing change in the adjective amplifier systems of Hong Kong, Philippine, and Indian English - Part 2"
author: Martin Schweinberger
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: 
  word_document:
    fig_caption: yes
    pandoc_args: --smart
bibliography: D:\\BibTex/Bibliography.bib
---

# Introduction{-}

This document shows an analysis of adjective amplification in Irish English based on the Irish component of the International Corpus of English (ICE). 

# Preparation{-}

In a first step, the session is prepared by clearing the work space, setting options, activating packages and functions, as well as loading relevant functions.

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
# clean current workspace
rm(list=ls(all=T))                                      
# establish version control
library(packrat)
# initialize packrat
#init()
# load packages
library(tidyverse)  
library(Boruta)
library(mlogit)
library(nnet)
# set options
options(stringsAsFactors = F)                           
options(scipen = 999) 
options(max.print=10000)
# define image directory
imageDirectory <- "images"   
```

# Load data{-}

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- read.delim("D:\\Uni\\Projekte\\02-Intensification\\AmpHKPIE\\data\\editdata//iceamp_04_clean.txt", sep = "\t", header = T)
# inspect
head(ice)
```

# Clean data

## Factorize predictors

## Scale frequency

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  select(-Id, -Correction, -SpeechUnit, -SpeechUnitCount, -PreContext, -Token, 
         -PostContext, -PreContextLong, -Amplified) %>%
  dplyr::mutate(Frequency = as.vector(scale(Frequency)),
                Gender = factor(Gender),
                Nationality = factor(Nationality),
                L1 = factor(L1),
                EducationLevel = factor(EducationLevel),
                Priming = factor(Priming),
                Emotionality = factor(Emotionality),
                Function = factor(Function),
                Ethnicity = factor(Ethnicity),
                OtherLanguages = factor(OtherLanguages),
                Birthplace = factor(Birthplace),
                SemanticCategory = factor(SemanticCategory),
                Speaker = paste0(File, "$", Speaker)) %>%
  select(-File, -Speaker, -WordCount)
str(ice)
```

Determine adjective frequency

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
fadj <- names(table(ice$Adjective))[which(table(ice$Adjective) > 5)]
fadj
```

Determine variant frequency

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
famp <- names(table(ice$Variant))[which(table(ice$Variant) > 20)]
famp
```
Collapse infrequent adjectives and amplifiers

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  mutate(Adjective = ifelse(Adjective %in% fadj, Adjective, "other"),
         Variant = ifelse(Variant %in% famp, Variant, "other"),
         Adjective = factor(Adjective),
         Variant = factor(Variant))
str(ice)
```

# Variant by Corpus and Age

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice %>%
  mutate(Age = ifelse(Age == "16-25"|Age == "17-25"|Age == "18-25", 3, 
               ifelse(Age == "26-40"|Age == "26-41", 2, 
               ifelse(Age == "41+"|Age == "42+", 1, Age))),
         Corpus = ifelse(Corpus == "ICE-HK", "ICE Hong Kong",
                  ifelse(Corpus == "ICE-IND", "ICE India", "ICE Philippines"))) %>%
  group_by(Corpus, Age, Variant) %>%
  summarise(Frequency = n()) %>%
  group_by(Corpus, Age) %>%
  mutate(AllSlots = sum(Frequency),
         Percent = round(Frequency/AllSlots*100, 1)) %>%
  select(-Frequency, -AllSlots) %>%
  ggplot(aes(x = Age, y = Percent, 
             group = Variant, color = Variant, linetype = Variant)) +
  facet_grid(cols = vars(Corpus)) +
  geom_line() + 
  coord_cartesian(ylim = c(0, 100)) +
  theme_set(theme_bw(base_size = 10)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  scale_color_manual(breaks = c("other", "pretty", "really", 
                                "so", "totally", "very"),
                     values = c("gray70", "gray60", "gray50", 
                                "gray40", "gray30", "gray20")) +
  scale_linetype_manual(breaks = c("other", "pretty", "really", 
                                   "so", "totally", "very"),
                        values = c(6, 5, 4, 3, 2, 1)) + 
  scale_x_discrete(breaks = 1:3, 
                   labels = c("41+", "26-41", "16-25")) +
  ggsave(file = 
           "D:\\Uni\\Projekte\\02-Intensification\\AmpHKPIE\\images/VariantAgeCorpus.png",
         height = 4,  width = 6, dpi = 320)
  
```

# Variant by Corpus and Age and Function

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice %>%
  mutate(Age = ifelse(Age == "16-25"|Age == "17-25"|Age == "18-25", 3, 
               ifelse(Age == "26-40"|Age == "26-41", 2, 
               ifelse(Age == "41+"|Age == "42+", 1, Age))),
         Corpus = ifelse(Corpus == "ICE-HK", "ICE Hong Kong",
                  ifelse(Corpus == "ICE-IND", "ICE India", "ICE Philippines"))) %>%
  group_by(Corpus, Age, Variant, Function) %>%
  summarise(Frequency = n()) %>%
  group_by(Corpus, Age, Function) %>%
  mutate(AllSlots = sum(Frequency),
         Percent = round(Frequency/AllSlots*100, 1)) %>%
  select(-Frequency, -AllSlots) %>%
  ggplot(aes(x = Age, y = Percent, 
             group = Variant, color = Variant, linetype = Variant)) +
  facet_grid(cols = vars(Corpus), rows=vars(Function)) +
  geom_line() + 
  coord_cartesian(ylim = c(0, 100)) +
  theme_set(theme_bw(base_size = 10)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  scale_color_manual(breaks = c("other", "pretty", "really", 
                                "so", "totally", "very"),
                     values = c("gray70", "gray60", "gray50", 
                                "gray40", "gray30", "gray20")) +
  scale_linetype_manual(breaks = c("other", "pretty", "really", 
                                   "so", "totally", "very"),
                        values = c(6, 5, 4, 3, 2, 1)) + 
  scale_x_discrete(breaks = 1:3, 
                   labels = c("41+", "26-41", "16-25")) +
  ggsave(file = 
           "D:\\Uni\\Projekte\\02-Intensification\\AmpHKPIE\\images/VariantAgeCorpusFunction.png",
         height = 4,  width = 6, dpi = 320)
  
```


# Split data by corpus

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
hk <- ice %>%
  filter(Corpus == "ICE-HK") %>%
  select(-Corpus)
# inspect
head(hk)
```

Remove NA

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
nrow(hk)
hk <- hk %>%
  na.omit()
nrow(hk)
```

# Boruta

Identify variables to include in regression modeling.

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
# create data for boruta
borutadata_hk <- hk
# run 1
set.seed(2020082401)
boruta_hk <- Boruta(Variant ~., data = borutadata_hk, maxRuns = 1000)
print(boruta_hk)
```

Boruta: second run

Remove variables confirmed non-important + next run

```{r amphkpie_02_11, echo=T, eval = T, message=FALSE, warning=FALSE}
# create vector of variables deemed not important
rejected <- names(boruta_hk$finalDecision)[which(boruta_hk$finalDecision == "Rejected")]
# update data for boruta
borutadata_hk <- borutadata_hk %>%
  dplyr::select(-rejected)
# run 2
set.seed(2020082402)
boruta_hk <- Boruta(Variant ~., data = borutadata_hk, maxRuns = 1000)
print(boruta_hk)
```

Visualize Boruta

```{r amphkpie_02_15, echo=T, eval = T, message=FALSE, warning=FALSE}
png("D:\\Uni\\Projekte\\02-Intensification\\AmpHKPIE\\images/Boruta_hk.png",  width = 1500, height = 750)
par(mar = c(18, 8, 4, 2) + 0.1)
plot(boruta_hk, cex.axis=2, las=2, xlab="", ylab = "", cex = 2, 
     col = c(rep("grey50", 15), rep("grey90",3)))
abline(v = 3.5, lty = "dashed")
mtext("Predictors", 1, line = 16, at = 7, cex = 3)
mtext("Control", 1, line = 16, at = 2, cex = 3)
mtext("Importance", 2, line = 2.5, at = 5, cex = 3, las = 0)
dev.off()
plot(boruta_hk, cex.axis=2, las=2, xlab="", ylab = "", cex = 2, 
     col = c(rep("grey50", 15), rep("grey90",3)))
abline(v = 3.5, lty = "dashed")
mtext("Predictors", 1, line = 16, at = 7, cex = 3)
mtext("Control", 1, line = 16, at = 2, cex = 3)
mtext("Importance", 2, line = 2.5, at = 5, cex = 3, las = 0)
par(mar = c(5, 4, 4, 2) + 0.1)
```

# Regression analysis

Load packages, set options, create base-line fixed-effects models

```{r amphkpie_02_21, echo=T, eval = T, message=FALSE, warning=FALSE}
# load library
library(rms)
library(car)
# set options
hkdf <- as.data.frame(hk)
options(contrasts  =c("contr.treatment", "contr.poly"))
hkdf_dist <- datadist(hkdf)
options(datadist = "hkdf_dist")
# generate initial minimal regression model 
m0 = multinom(Variant ~ 1, data = hkdf)
# inspect results
summary(m0)
```

## Model fitting{-}

Step-wise step-up

```{r amphkpie_02_23, echo=T, eval = T, message=FALSE, warning=FALSE}
# extract AICs
aic.m0 <- AIC(logLik(m0))
# inspect AICs
aic.m0
```

Automated model fitting

```{r amphkpie_02_27, echo=T, eval = T, message=FALSE, warning=FALSE}
library(MASS)
# Fit the full model 
#full.model <- multinom(Variant ~ (Date + Gender + Age + Nationality + L1 + EducationLevel + OtherLanguages + Birthplace + Ethnicity + Adjective + Variant + Function + Frequency + Priming + Gradability + SemanticCategory + Emotionality)^3, data = hkdf)
# Stepwise regression model
step.model <- step(m0, scope = . ~ .^3, direction = "both", trace = FALSE)
summary(step.model)
```

Create final model

```{r amphkpie_02_27, echo=T, eval = T, message=FALSE, warning=FALSE}
mf_hk <- multinom(Variant ~ (Date + Gender + Age + Nationality + L1 + EducationLevel + OtherLanguages + Birthplace + Ethnicity + Adjective + Variant + Function + Frequency + Priming + Gradability + SemanticCategory + Emotionality)^3, data = hkdf)
```

Visualize effects

```{r amphkpie_02_27, echo=T, eval = T, message=FALSE, warning=FALSE}
library(effects)
png("D:\\Uni\\Projekte\\02-Intensification\\AmpHKPIE\\images/effectsfinalmodel.png",  width = 960, height = 480) 
plot(allEffects(mf_hk), type="response", ylim=c(0,1), grid=TRUE, 
     lines = list(col="black",
                  lty = 1,
                  confint=list(style="bars",
                               col = "grey80")), 
     ylab = "Probability")
dev.off()
plot(allEffects(mf_hk), type="response", ylim=c(0,1), grid=TRUE, 
     lines = list(col="black",
                  lty = 1,
                  confint=list(style="bars",
                               col = "grey80")), 
     ylab = "Probability")
```






