---
title: "A corpus-based analysis of ongoing change in the adjective amplifier systems of Hong Kong, Philippine, and Indian English - Part 2"
author: Martin Schweinberger
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: 
  word_document:
    fig_caption: yes
    pandoc_args: --smart
bibliography: D:\\BibTex/Bibliography.bib
---

# Introduction{-}

This document shows an analysis of adjective amplification in Irish English based on the Irish component of the International Corpus of English (ICE). 

# Preparation{-}

In a first step, the session is prepared by clearing the work space, setting options, activating packages and functions, as well as loading relevant functions.

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
# clean current workspace
rm(list=ls(all=T))                                      
# establish version control
library(packrat)
# initialize packrat
#init()
# load packages
library(tidyverse)  
library(Boruta)
library(mlogit)
library(nnet)
# set options
options(stringsAsFactors = F)                           
options(scipen = 999) 
options(max.print=10000)
# define image directory
imageDirectory <- "images"   
```

# Load data{-}

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- read.delim("D:\\Uni\\Projekte\\02-Intensification\\AmpHKPIE\\data\\editdata//iceamp_04_clean.txt", sep = "\t", header = T)
# inspect
head(ice)
```

# Clean data

## Factorize predictors

## Scale frequency

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  select(-Id, -Correction, -SpeechUnit, -SpeechUnitCount, -PreContext, -Token, -L1, 
         -PostContext, -PreContextLong, -Amplified, -Nationality, -OtherLanguages, -Birthplace) %>%
  dplyr::mutate(Frequency = as.vector(scale(Frequency)),
                Gender = factor(Gender),
                EducationLevel = factor(EducationLevel),
                Priming = factor(Priming),
                Emotionality = factor(Emotionality),
                Function = factor(Function),
                Ethnicity = factor(Ethnicity),
                SemanticCategory = factor(SemanticCategory),
                Speaker = paste0(File, "$", Speaker)) %>%
  select(-File, -WordCount)
str(ice)
```

Determine adjective frequency

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
fadj <- names(table(ice$Adjective))[which(table(ice$Adjective) > 15)]
fadj
```

Determine variant frequency

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
famp <- names(table(ice$Variant))[which(table(ice$Variant) > 50)]
famp
```
Collapse infrequent adjectives and amplifiers

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  mutate(Adjective = ifelse(Adjective %in% fadj, Adjective, "other"),
         Variant = ifelse(Variant %in% famp, Variant, "other"),
         Adjective = factor(Adjective),
         Variant = factor(Variant)) %>%
  group_by(Corpus) %>%
  mutate(Frequency = scale(Frequency))
str(ice)
```

# Variant by Corpus and Age

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice %>%
  mutate(Age = ifelse(Age == "16-25"|Age == "17-25"|Age == "18-25", 3, 
               ifelse(Age == "26-40"|Age == "26-41", 2, 
               ifelse(Age == "41+"|Age == "42+", 1, Age))),
         Corpus = ifelse(Corpus == "ICE-HK", "ICE Hong Kong",
                  ifelse(Corpus == "ICE-IND", "ICE India", "ICE Philippines"))) %>%
  group_by(Corpus, Age, Variant) %>%
  summarise(Frequency = n()) %>%
  group_by(Corpus, Age) %>%
  mutate(AllSlots = sum(Frequency),
         Percent = round(Frequency/AllSlots*100, 1)) %>%
  select(-Frequency, -AllSlots) %>%
  ggplot(aes(x = Age, y = Percent, 
             group = Variant, color = Variant, linetype = Variant)) +
  facet_grid(cols = vars(Corpus)) +
  geom_line() + 
  coord_cartesian(ylim = c(0, 100)) +
  theme_set(theme_bw(base_size = 10)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  scale_color_manual(breaks = c("other", "really", "so", "very"),
                     values = c("gray80", "gray60", "gray40", "gray20")) +
  scale_linetype_manual(breaks = c("other", "really", "so", "very"),
                        values = c(4, 3, 2, 1)) + 
  scale_x_discrete(breaks = 1:3, 
                   labels = c("41+", "26-41", "16-25")) +
  ggsave(file = 
           "D:\\Uni\\Projekte\\02-Intensification\\AmpHKPIE\\images/VariantAgeCorpus.png",
         height = 4,  width = 6, dpi = 320)
  
```

# Variant by Corpus and Age and Function

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice %>%
  mutate(Age = ifelse(Age == "16-25"|Age == "17-25"|Age == "18-25", 3, 
               ifelse(Age == "26-40"|Age == "26-41", 2, 
               ifelse(Age == "41+"|Age == "42+", 1, Age))),
         Corpus = ifelse(Corpus == "ICE-HK", "ICE Hong Kong",
                  ifelse(Corpus == "ICE-IND", "ICE India", "ICE Philippines"))) %>%
  group_by(Corpus, Age, Variant, Function) %>%
  summarise(Frequency = n()) %>%
  group_by(Corpus, Age, Function) %>%
  mutate(AllSlots = sum(Frequency),
         Percent = round(Frequency/AllSlots*100, 1)) %>%
  select(-Frequency, -AllSlots) %>%
  ggplot(aes(x = Age, y = Percent, 
             group = Variant, color = Variant, linetype = Variant)) +
  facet_grid(cols = vars(Corpus), rows=vars(Function)) +
  geom_line() + 
  coord_cartesian(ylim = c(0, 100)) +
  theme_set(theme_bw(base_size = 10)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  scale_color_manual(breaks = c("other", "really", "so", "very"),
                     values = c("gray80", "gray60", "gray40", "gray20")) +
  scale_linetype_manual(breaks = c("other", "really", "so", "very"),
                        values = c(4, 3, 2, 1)) +  
  scale_x_discrete(breaks = 1:3, 
                   labels = c("41+", "26-41", "16-25")) +
  ggsave(file = 
           "D:\\Uni\\Projekte\\02-Intensification\\AmpHKPIE\\images/VariantAgeCorpusFunction.png",
         height = 4,  width = 6, dpi = 320)
  
```
# PHI{-}

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
phi <- ice %>%
  ungroup() %>%
  filter(Corpus == "ICE-PHI") %>%
  select(-Corpus, -Speaker, -Ethnicity) %>%
  droplevels()
# inspect
head(phi)
```

Remove NA

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
nrow(phi)
phi <- phi %>%
  na.omit() %>%
  mutate(Age = factor(Age),
         Date = ifelse(Date == "1991"|Date == "1992", "Before 1993", "After 1998"),
         Date = factor(Date, levels = c("Before 1993", "After 1998")))
  
nrow(phi)
```

# Random forest

Identify variables to include in regression modeling.

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
library(randomForest)
set.seed(2020082401)
rf_phi <- randomForest(Variant ~., data = phi, ntree=3000, proximity=TRUE, importance=TRUE)
# inspect rf results
rf_phi 
```

Plot out-of-bag error frequency

```{r l2amp_03_21, echo=T, eval = T, message=FALSE, warning=FALSE}
# plot new precision/error rate
oob.error.data <- data.frame(
  Trees=rep(1:nrow(rf_phi$err.rate), times=5),
  Type=rep(c("OOB", "other", "really", "so", "very"), each=nrow(rf_phi$err.rate)),
  Error=c(rf_phi$err.rate[,"OOB"],
          rf_phi$err.rate[,"other"],
          rf_phi$err.rate[,"really"],
          rf_phi$err.rate[,"so"],
          rf_phi$err.rate[,"very"]))
ggplot(data=oob.error.data, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))
```

Now, we check the error rates and accuracy and also check how much the model performs better than a base-line model.

```{r l2amp_03_23, echo=T, eval = T, message=FALSE, warning=FALSE}
# determine accuracy by prediction
library(caret)
# prediction
pnsrf <- predict(rf_phi, phi)
confusionMatrix(pnsrf, phi$Variant)
# calculate increase in prediction accuracy compared to base-line model
cm <- confusionMatrix(pnsrf, phi$Variant)
round(cm[3]$overall[[1]]/cm[3]$overall[[5]]*100, 2) - 100
```

Now, we inspect which variables are important for the predictions.

```{r l2amp_03_33, echo=T, eval = T, message=FALSE, warning=FALSE}
png("D:\\Uni\\Projekte\\02-Intensification\\AmpHKPIE\\images//VarImp_IcePhi.png",  width = 700, height = 500) # save plot
varImpPlot(rf_phi, main = "", pch = 20, cex = 1.5) 
dev.off()
varImpPlot(rf_phi, main = "", pch = 20, cex = 1.5)
```

# Prediction


```{r amphkpie_02_21, echo=T, eval = T, message=FALSE, warning=FALSE}
pphi_rf <- predict(rf_phi, phi, type = "prob")
phi_pred <- cbind(phi, pphi_rf)
pphi <- phi_pred %>%
  gather(PredictedVariant, Probability, other:very)
# inspect
head(pphi)

```


```{r amphkpie_02_21, echo=T, eval = T, message=FALSE, warning=FALSE}
pphi %>%
  select(Age, Probability, Function, Gender, PredictedVariant) %>%
  mutate(Age = ifelse(Age == "16-25", 3, 
               ifelse(Age == "26-40", 2, 
               ifelse(Age == "41+", 1, Age)))) %>%
  group_by(Age, Function, Gender, PredictedVariant) %>%
  summarise(Probability = mean(Probability)) %>%
  ggplot(aes(x = Age, y = Probability, 
             group = PredictedVariant, color = PredictedVariant, linetype = PredictedVariant)) +
  geom_line() + 
  facet_grid(cols = vars(Gender), rows = vars(Function)) +
  theme_set(theme_bw(base_size = 10)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  scale_color_manual(breaks = c("other", "really", "so", "very"),
                     values = c("gray80", "gray60", "gray40", "gray20")) +
  scale_linetype_manual(breaks = c("other", "really", "so", "very"),
                        values = c(4, 3, 2, 1)) +  
  scale_x_continuous(breaks = 1:3, 
                   labels = c("41+", "26-40", "16-25")) +
  ggsave(file = 
         "D:\\Uni\\Projekte\\02-Intensification\\AmpHKPIE\\images/VariantAgeFunction_Prob_Phi.png",
         height = 4,  width = 6, dpi = 320)
```

```{r amphkpie_02_21, echo=T, eval = T, message=FALSE, warning=FALSE}
pphi %>%
  select(Date, Probability, Function, Gender, PredictedVariant) %>%
  group_by(Date, Function, Gender, PredictedVariant) %>%
  summarise(Probability = mean(Probability)) %>%
  ggplot(aes(x = Date, y = Probability, 
             group = PredictedVariant, color = PredictedVariant, linetype = PredictedVariant)) +
  geom_smooth(se = F, span = 1) + 
  facet_grid(cols = vars(Gender), rows = vars(Function)) +
  theme_set(theme_bw(base_size = 10)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  scale_color_manual(breaks = c("other", "really", "so", "very"),
                     values = c("gray80", "gray60", "gray40", "gray20")) +
  scale_linetype_manual(breaks = c("other", "really", "so", "very"),
                        values = c(4, 3, 2, 1)) +  
  ggsave(file = 
         "D:\\Uni\\Projekte\\02-Intensification\\AmpHKPIE\\images/VariantDateFunction_Prob_Phi.png",
         height = 4,  width = 6, dpi = 320)
```











